Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach

### 2024-11-02 paper/paper.qmd
Fixed bugs and rendered

swing_state_results <- intercept_wide %>%
  mutate(Winner = ifelse(difference > 0, "Harris", "Trump")) %>%
  group_by(Winner) %>%
  summarize(Predicted_Swing_State_Votes = sum(electoral_votes))

>>>>

swing_state_results <- intercept_wide %>%
  mutate(Winner = ifelse(Difference > 0, "Harris", "Trump")) %>%
  group_by(Winner) %>%
  summarize(Predicted_Swing_State_Votes = sum(Votes))
